---
title: "REPORT"
output: pdf_document
params:
  gVars: NA
  input: NA
---

```{r check_norm, echo=F}
isNorm <- !is.null(params$gVars$norm.data)
```

```{r check_comb, echo=F}
isCorr <- !is.null(params$gVars$comb.data)
```

```{r check_agg, echo=F}
isAgg <- !is.null(params$gVars$agg.data)
```

```{r check_deg, echo=F}
isDeg <- !is.null(params$gVars$deg.list)
```

```{r check_heat_comps, echo=F}
isComps <- !is.null(params$input$heatComps)
```

```{r check_heat_conitions, echo=F}
isConds <- !is.null(params$input$conditionsHeat)
```

```{r check_expr, echo=F}
isExpr <- !is.null(params$gVars$expr.data)
```

# Box Plot

## Before Normalization

<!-- ```{r boxplot_before_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm} -->
```{r boxplot_before_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm}
if(isNorm){
        #filt.data <- params$gVars$filt.data()
        filt.data <- params$gVars$filt.data
        if(params$input$arrType=="af_exp"){
                print("No plot for Affymetrix data!")
        }else if(params$input$arrType=="il_methyl"){
                filt.data <- minfi::preprocessRaw(filt.data)
                filt.data <- minfi::getMethSignal(filt.data, "M")
                par(cex.axis=0.5)
                boxplot(filt.data, las=2, cex=0.7, main="Before Normalization")
        }else{
                par(cex.axis=0.5)
                boxplot(log2(filt.data), las=2, cex=0.7, main="Before Normalization")
        }
}else{
        print("Normalized data not found!")
}
```

## After Normalization

<!-- ```{r boxplot_after_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm} -->
```{r boxplot_after_normalization, echo=F, fig.height=4, fig.width=9}
if(isNorm){
        norm.data <- params$gVars$norm.data
        par(cex.axis=0.5)
        boxplot(norm.data, las=2, cex=0.7, main="After Normalization")
}else{
        print("Normalized data not found!")
}
```

# Density Plot

## Before Normalization

<!-- ```{r density_before_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm} -->
```{r density_before_normalization, echo=F, fig.height=4, fig.width=9}
if(isNorm){
        if(params$input$arrType=="af_exp"){
                print("No plot for Affymetrix data!")
        }else if(params$input$arrType=="ag_exp1"){
                print("No plot for Agilent single color data!")
        }else if(params$input$arrType=="il_methyl"){
                RGset <- params$gVars$RGset
                minfi::densityPlot(RGset, main="Before Normalization", xlab="Beta")
        }else{
                rgList <- params$gVars$rgList
                plotDensities(rgList, main="Before Normalization")
        }
}else{
        print("Normalized data not found!")
}
```

## After Normalization

<!-- ```{r density_after_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm} -->
```{r density_after_normalization, echo=F, fig.height=4, fig.width=9}
if(isNorm){
        if(params$input$arrType=="af_exp"){
                print("No plot for Affymetrix data!")
        }else if(params$input$arrType=="ag_exp1"){
                print("No plot for Agilent single color data!")
        }else if(params$input$arrType=="il_methyl"){
                Mset <- params$gVars$Mset
                if(is(Mset, "RGChannelSet") || is(Mset, "MethylSet")){
                        minfi::densityPlot(Mset, main="After Normalization", xlab="Beta")
                }else{
                        print("No plot for this nomalization method!")
                }
        }else{
                rgList.norm <- params$gVars$rgList.norm
                plotDensities(rgList.norm, main="After Normalization")
        }
}else{
        print("Normalized data not found!")
}
```

# Mean-Difference Plot

## Before Normalization

<!-- ```{r MD_before_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm} -->
```{r MD_before_normalization, echo=F, fig.height=4, fig.width=9}
if(isNorm){
        if(params$input$arrType=="af_exp"){
                print("No plot for Affymetrix data!")
        }else if(params$input$arrType=="ag_exp1"){
                print("No plot for Agilent single color data!")
        }else if(params$input$arrType=="il_methyl"){
                print("No plot for Illumina methylation data!")
        }else{
                rgList <- params$gVars$rgList
                plotMD(rgList, main="Before Normalization")
        }
}else{
        print("Normalized data not found!")
}
```

## After Normalization

<!-- ```{r MD_after_normalization, echo=F, fig.height=4, fig.width=9, eval=isNorm} -->
```{r MD_after_normalization, echo=F, fig.height=4, fig.width=9}
if(isNorm){
        if(params$input$arrType=="af_exp"){
                print("No plot for Affymetrix data!")
        }else if(params$input$arrType=="ag_exp1"){
                print("No plot for Agilent single color data!")
        }else if(params$input$arrType=="il_methyl"){
                print("No plot for Illumina methylation data!")
        }else{
                rgList.norm <- params$gVars$rgList.norm
                plotMD(rgList.norm, main="After Normalization")
        }
}else{
        print("Normalized data not found!")
}
```

# Confounding Plot

<!-- ```{r confounding_after_normalization, echo=F, fig.height=9, fig.width=9, eval=isNorm} -->
```{r confounding_after_normalization, echo=F, fig.height=9, fig.width=9}
if(isNorm){
        ph <- params$gVars$phTable
        #ph <- as.data.frame(apply(ph, 2, factor))
        phFactor <- params$gVars$phFactor
        test <- sapply(colnames(ph), function(b) length(table(ph[,b])) > 1 & length(table(ph[,b])) != length(ph[,b]))
        #ph <- ph[,test]
        phFactor <- phFactor[,test]
        if(!is.null(params$gVars$svaStep)){
                if(params$gVars$svaStep==1){
                        svaSV <- as.data.frame(apply(params$gVars$svaSV, 2, factor))
                        svaSVc <- params$gVars$svaSVc
                        phFactor <- cbind(phFactor, svaSV, svaSVc) 
                }
        }
        #res <- confounding(ph, margins = c(15,15), notecex=0.5)
        res <- confounding(phFactor, margins = c(15,15), notecex=0.5)
}else{
        print("Normalized data not found!")
}
```

# Prince Plot

## After Normalization

<!-- ```{r prince_after_normalization, echo=F, fig.height=9, fig.width=9, eval=isNorm} -->
```{r prince_after_normalization, echo=F, fig.height=9, fig.width=9}
if(isNorm){
        ph <- params$gVars$phTable
        rownames(ph) <- ph[,params$gVars$sampleColID]
        phFactor <- params$gVars$phFactor
        rownames(phFactor) <- ph[,params$gVars$sampleColID]
        data <- params$gVars$norm.data
        npc <- 10
        test <- sapply(colnames(ph), function(b) length(table(ph[,b])) > 1 & length(table(ph[,b])) != length(ph[,b]))
        #ph <- as.data.frame(apply(ph, 2, factor))
        #ph <- ph[,test]
        phFactor <- phFactor[,test]
        if(!is.null(params$gVars$svaStep)){
                if(params$gVars$svaStep==1){
                        svaSV <- as.data.frame(apply(params$gVars$svaSV, 2, factor))
                        svaSVc <- params$gVars$svaSVc
                        #ph <- cbind(ph, svaSV) 
                        phFactor <- cbind(phFactor, svaSV, svaSVc) 
                }
        }
        if(npc>ncol(data)){
                npc <- ncol(data)
        }
        #pr <- prince(data, ph, top=npc)
        pr <- prince(data, phFactor, top=npc)
        # generate the prince plot
        prince.plot(prince=pr, margins=c(15,15), note=TRUE, notecex=0.5)
}else{
        print("Normalized data not found!")
}
```

## After Correction

<!-- ```{r prince_after_correction, echo=F, fig.height=9, fig.width=9, eval=isCorr} -->
```{r prince_after_correction, echo=F, fig.height=9, fig.width=9}
if(isCorr){
        ph <- params$gVars$phTable
        rownames(ph) <- ph[,params$gVars$sampleColID]
        phFactor <- params$gVars$phFactor
        rownames(phFactor) <- ph[,params$gVars$sampleColID]
        #ph <- as.data.frame(apply(ph, 2, factor))
        data <- params$gVars$comb.data
        npc <- 10
        test <- sapply(colnames(ph), function(b) length(table(ph[,b])) > 1 & length(table(ph[,b])) != length(ph[,b]))
        phFactor <- phFactor[,test]
        if(!is.null(params$gVars$svaStep)){
                if(params$gVars$svaStep==1){
                        svaSV <- as.data.frame(apply(params$gVars$svaSV, 2, factor))
                        svaSVc <- params$gVars$svaSVc
                        #ph <- cbind(ph, svaSV) 
                        phFactor <- cbind(phFactor, svaSV, svaSVc) 
                }
        }
        if(npc>ncol(data)){
                npc <- ncol(data)
        }
        #pr <- prince(data, ph[,test], top=npc)
        pr <- prince(data, phFactor, top=npc)
        #generate the prince plot
        prince.plot(prince=pr, margins = c(5,5), note=TRUE, notecex=0.5)
}else{
        print("Corrected data not found!")
}
```

# Hierarchical Clustering

## After Normalization

<!-- ```{r HC_after_normalization, echo=F, fig.height=9, fig.width=9, eval=isNorm} -->
```{r HC_after_normalization, echo=F, fig.height=9, fig.width=9}
if(isNorm){
        ph <- params$gVars$phTable
        rownames(ph) <- ph[,params$gVars$sampleColID]
        phFactor <- params$gVars$phFactor
        rownames(phFactor) <- ph[,params$gVars$sampleColID]
        data <- params$gVars$norm.data
        colnames(data) <- rownames(ph)
        test <- sapply(colnames(ph), function(b) length(table(ph[,b])) > 1 & length(table(ph[,b])) != length(ph[,b]))
        #ph <- as.data.frame(apply(ph, 2, factor))
        #ph <- ph[,test]
        phFactor <- phFactor[,test]
        if(!is.null(params$gVars$svaStep)){
                if(params$gVars$svaStep==1){
                        svaSV <- as.data.frame(apply(params$gVars$svaSV, 2, factor))
                        svaSVc <- params$gVars$svaSVc
                        #ph <- cbind(ph, svaSV) 
                        phFactor <- cbind(phFactor, svaSV, svaSVc) 
                }
        }
        #hc plot
        #hca.plot(data, ph, method="correlation")
        hca.plot(data, phFactor, method="correlation")
}else{
        print("Normalized data not found!")
}
```

## After Correction

<!-- ```{r HC_known_corrected, echo=F, fig.height=9, fig.width=9, eval=isCorr} -->
```{r HC_known_corrected, echo=F, fig.height=9, fig.width=9}
if(isCorr){
        ph <- params$gVars$phTable
        rownames(ph) <- ph[,params$gVars$sampleColID]
        phFactor <- params$gVars$phFactor
        rownames(phFactor) <- ph[,params$gVars$sampleColID]
        data <- params$gVars$comb.data
        colnames(data) <- rownames(ph)
        test <- sapply(colnames(ph), function(b) length(table(ph[,b])) > 1 & length(table(ph[,b])) != length(ph[,b]))
        phFactor <- phFactor[,test]
        if(!is.null(params$gVars$svaStep)){
                if(params$gVars$svaStep==1){
                        svaSV <- as.data.frame(apply(params$gVars$svaSV, 2, factor))
                        svaSVc <- params$gVars$svaSVc
                        phFactor <- cbind(phFactor, svaSV, svaSVc) 
                }
        }
        # hc plot
        #ph <- as.data.frame(apply(ph, 2, factor))
        #hca.plot(data, ph[,test], method = "correlation")
        hca.plot(data, phFactor, method = "correlation")
}else{
        print("Corrected data not found!")
}
```

# Multidimensional Scaling Plot

## Before Correction

<!-- ```{r MDS_before_correction, echo=F, fig.height=9, fig.width=9, eval=isNorm} -->
```{r MDS_before_correction, echo=F, fig.height=9, fig.width=9}
if(isNorm){
        if(!is.null(params$input$mdsLabel) && !is.null(params$input$mdsColor)){
                norm.data <- params$gVars$norm.data
                phTable <- params$gVars$phTable
                #phTable <- as.data.frame(apply(phTable, 2, factor))
                phFactor <- params$gVars$phFactor
                percTop <- 1
                topNum <- floor((nrow(norm.data)*percTop)/100)
                ##limma:::plotMDS(norm.data, top=500, labels=phTable[,params$input$mdsLabel], col=as.numeric(phTable[,params$input$mdsColor]), gene.selection="common", main = "Before removing any batch", cex=0.5)
                #limma:::plotMDS(norm.data, top=topNum, labels=phTable[,params$input$mdsLabel], col=as.numeric(phTable[,params$input$mdsColor]), gene.selection="common", main = "Before removing any batch", cex=0.5)
                limma:::plotMDS(norm.data, top=topNum, labels=as.character(phFactor[,params$input$mdsLabel]), col=as.numeric(phFactor[,params$input$mdsColor]), gene.selection="common", main="Before removing any batch", cex=0.5)
        }else{
                print("Missing label and color information...")
        }
}else{
        print("Normalized data not found!")
}
```

## After Correction

<!-- ```{r MDS_known_corrected, echo=F, fig.height=9, fig.width=9, eval=isCorr} -->
```{r MDS_known_corrected, echo=F, fig.height=9, fig.width=9}
if(isCorr){
        if(!is.null(params$input$mdsLabel) && !is.null(params$input$mdsColor)){
                comb.data <- params$gVars$comb.data
                phTable <- params$gVars$phTable
                #phTable <- as.data.frame(apply(phTable, 2, factor))
                phFactor <- params$gVars$phFactor
                percTop <- 1
                topNum <- floor((nrow(comb.data)*percTop)/100)
                ##limma:::plotMDS(comb.data, top=500, labels=phTable[,params$input$mdsLabel], col=as.numeric(phTable[,params$input$mdsColor]), gene.selection="common", main = "After removing batches", cex=0.5)
                #limma:::plotMDS(comb.data, top=topNum, labels=phTable[,params$input$mdsLabel], col=as.numeric(phTable[,params$input$mdsColor]), gene.selection="common", main = "After removing batches", cex=0.5)
                limma:::plotMDS(comb.data, top=topNum, labels=as.character(phFactor[,params$input$mdsLabel]), col=as.numeric(phFactor[,params$input$mdsColor]), gene.selection="common", main="After removing batches", cex=0.5)
        }else{
                print("Missing label and color information...")
        }
}else{
        print("Corrected data not found!")
}
```

## After Aggregation

<!-- ```{r MDS_after_aggregation, echo=F, fig.height=9, fig.width=9, eval=isAgg} -->
```{r MDS_after_aggregation, echo=F, fig.height=9, fig.width=9}
if(isAgg){
        if(!is.null(params$input$mdsLabel) && !is.null(params$input$mdsColor)){
                if(grepl("ag_exp.*", params$input$arrType)){
                        agg.data <- params$gVars$agg.data
                        phTable <- params$gVars$phTable
                        #phTable <- as.data.frame(apply(phTable, 2, factor))
                        phFactor <- params$gVars$phFactor
                        percTop <- 1
                        topNum <- floor((nrow(agg.data)*percTop)/100)
                        ##limma:::plotMDS(agg.data, top=500, labels=phTable[,params$input$mdsLabel], col=as.numeric(phTable[,params$input$mdsColor]), gene.selection="common", main = "After aggregation", cex=0.5)
                        #limma:::plotMDS(agg.data, top=topNum, labels=phTable[,params$input$mdsLabel], col=as.numeric(phTable[,params$input$mdsColor]), gene.selection="common", main = "After aggregation", cex=0.5)
                        limma:::plotMDS(agg.data, top=topNum, labels=as.character(phFactor[,params$input$mdsLabel]), col=as.numeric(phFactor[,params$input$mdsColor]), gene.selection="common", main="After aggregation", cex=0.5)
                }else{
                        print(paste0("No plot for ", params$input$arrType, " data!"))
                }
        }else{
                print("Missing label and color information...")
        }
}else{
        if(params$input$arrType=="af_exp"){
                print("No plot for Affymetrix data!")
        }else if(params$input$arrType=="il_methyl"){
                print("No plot for Illumina methylation data!")
        }else{
                print("Aggregation by annotation was not performed!")
        }
}
```

# Volcano Plot

<!-- ```{r volcano_plot, echo=F, fig.height=9, fig.width=9, eval=isDeg} -->
```{r volcano_plot, echo=F, fig.height=9, fig.width=9}
if(isDeg){
        p <- params$gVars$volGGplot()
        deg <- params$gVars$volDeg
        #adjPvThr <- -log10(as.numeric(params$input$adjPvThr))
        pvThr <- params$gVars$pvFilt
        lfc <- params$gVars$lfcFilt
        #degSel <- deg[deg$y>=adjPvThr & abs(deg$x)>=params$input$lfcThr,]
        degSel <- deg[deg$y>=pvThr & abs(deg$x)>=lfc,]

        p <- p +
        geom_point(data = degSel, color = "red") +
        scale_x_continuous("log2(Fold-change)", limits = range(-params$input$xAxis,params$input$xAxis)) +
        scale_y_continuous("-log10(P.Value)", limits = range(0,params$input$yAxis)) + theme_bw()

        if(params$input$gName){
            p <- p + geom_text_repel(
                    data = degSel,
                    aes(label = ID),
                    size = 5
            )
        }
        print(p)
}else{
        print("Differential results not found!")
}
```

# Venn Representation

```{r venn_plot, echo=F, fig.height=9, fig.width=9}
if(isDeg){
        deg.list <- params$gVars$deg.list
        #lfc <- as.numeric(params$input$lfcThr)
        #adjPv <- as.numeric(params$input$adjPvThr)
        lfc <- as.numeric(params$gVars$lfcFilt)
        #adjPv <- -log10(as.numeric(params$gVars$adjPvFilt))
        pvThr <- params$gVars$pvFilt
        pvType <- params$gVars$pvType
        intersectComps <- params$input$intersectComps

        deg.item.list <- list()
        #for(comp in names(deg.list)){
        for(comp in intersectComps){
                degDF <- deg.list[[comp]]
                #selVec <- which(-log10(degDF$adj.P.Val)>adjPv & abs(degDF$logFC)>lfc)
                selVec <- which(-log10(degDF[,pvType])>pvThr & abs(degDF$logFC)>lfc)

                if(length(selVec)==0)
                next

                deg.item.list[[comp]] <- rownames(degDF[selVec,])
        }

        if(length(deg.item.list)>1){
                if(length(deg.item.list)<=4){
                        fillCol <- c("blue", "red", "yellow", "green")
                        cat_label_size <- 1
                        area_label_size <- 2
                        cat_dist <- c(0.22,0.22,0.1,0.1)
                        printMode <- "raw"
                        marginSize <- 0.12
                        futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
                        venn.plot <- venn.diagram(
                                  x=deg.item.list,
                                  filename=NULL,
                                  cat.cex=cat_label_size,
                                  cat.dist=cat_dist[1:length(deg.item.list)],
                                  cex=area_label_size,
                                  fill=fillCol[1:length(deg.item.list)],
                                  margin=marginSize,
                                  print.mode=printMode
                        )
                        grid.draw(venn.plot)
                }else{
                        print("Too Many Sets for Venn Representation!")
                }
        }else{
                print("Not Enough Sets to Intersect!")
        }
}else{
        print("Differential results not found!")
}
```

# UpSet Representation

```{r upset_plot, echo=F, fig.height=9, fig.width=9}
if(isDeg){
        deg.list <- params$gVars$deg.list
        lfc <- as.numeric(params$gVars$lfcFilt)
        pvThr <- params$gVars$pvFilt
        pvType <- params$gVars$pvType
        intersectComps <- params$input$intersectComps

        deg.item.list <- list()
        #for(comp in names(deg.list)){
        for(comp in intersectComps){
                degDF <- deg.list[[comp]]
                #selVec <- which(-log10(degDF$adj.P.Val)>adjPv & abs(degDF$logFC)>lfc)
                selVec <- which(-log10(degDF[,pvType])>pvThr & abs(degDF$logFC)>lfc)

                if(length(selVec)==0)
                next

                deg.item.list[[comp]] <- rownames(degDF[selVec,])
        }

        if(length(deg.item.list)>1){
                deg.item.DF <- data.frame(genes=unique(unlist(deg.item.list)), stringsAsFactors=F)
                for(itm in names(deg.item.list)){
                        deg.item.DF[,itm] <- 0
                        deg.item.DF[which(deg.item.DF$genes %in% deg.item.list[[itm]]),itm] <- 1
                }
                setNames <- names(deg.item.list)
                setColors <- rep("gray23", length(deg.item.list))
                keepingOrder <- F
                textScale <- 1
                intersectSize <- 10
                xLabel <- "Set Size"
                upset(deg.item.DF, nintersects=intersectSize, sets=setNames, order.by="freq", decreasing=T, line.size=0.1, sets.x.label=xLabel, keep.order=keepingOrder, text.scale=textScale, sets.bar.color=setColors)
        }else{
                print("Not Enough Sets to Intersect!")
        }
}else{
        print("Differential results not found!")
}
```

# Expression Box Plot

<!-- ```{r expression_boxplot, echo=F, fig.height=9, fig.width=9, eval=isExpr} -->
```{r expression_boxplot, echo=F, fig.height=9, fig.width=9}
if(isExpr){
        data <- params$gVars$expr.data
        #varI <- params$input$varILimma
        varI <- params$input$varIBoxPlot
        phTable <- params$gVars$phTable
        genes <- params$input$expGenes
        conditions <- params$input$conditions

        isCond <-TRUE 
        if(is.null(conditions) || is.na(conditions) || conditions=="NA")
        isCond <- FALSE 

        if(isCond){
                if(length(genes)>=1){
                        dataCols <- as.integer(gsub("X", "", colnames(data)))
                        dataColsVarI <- phTable[,varI]

                        tmp.data <- data
                        colnames(tmp.data) <- dataColsVarI

                        selCols <- which(colnames(tmp.data) %in% conditions)
                        selRows <- which(rownames(tmp.data) %in% genes)
                        melted.tmp.data <- melt(tmp.data[selRows, selCols])
                        if(ncol(melted.tmp.data)==1){
                                melted.tmp.data <- data.frame(Var1=rownames(tmp.data)[selRows], Var2=colnames(tmp.data)[selCols], value=melted.tmp.data, stringsAsFactors=F)
                        }
                        p <- ggplot(melted.tmp.data, aes(x=Var2, y=value, fill=Var2)) +
                        geom_boxplot() +
                        geom_jitter(aes(Var2,value),
                                position=position_jitter(width=0.1,height=0),
                                alpha=0.6,
                                size=3,
                        show.legend=FALSE) +
                        facet_grid(.~Var1, scales="free") +
                        labs(x="Condition", y="Expression Values") +
                        scale_fill_discrete(name="Condition") +
                        theme(panel.grid.minor = element_blank(), panel.grid.major.y = element_blank(), panel.grid.major.x = element_blank(), panel.background = element_rect(fill='#f5f5f5', color='#e8e8e8'), axis.text.x=element_text(angle=90, hjust=1))
                        p
                }else{
                        print("Need at least 1 gene to create boxplot!")
                }
        }else{
                print("No conditions provided!")
        }
}else{
        print("Normalized expression matrix not found!")
}
```

# Expression Heatmap

<!-- ```{r expression_heatmap, echo=F, fig.height=9, fig.width=9, eval=isDeg} -->
```{r expression_heatmap, echo=F, fig.height=9, fig.width=9}
if(isDeg && isComps && isConds){
        deg.list <- params$gVars$deg.list
        data <- params$gVars$expr.data

        varI <- params$input$varILimma
        phTable <- params$gVars$phTable
        percDE <- params$input$percDE
        comps <- params$input$heatComps
        conditions <- params$input$conditionsHeat

        uq <- (100-(percDE/2))/100
        lq <- (percDE/2)/100

        deList <- list()
        for(comp in comps){
                deg.list.comp <- deg.list[[comp]]
                qVals <- quantile(deg.list.comp$score, probs=c(lq, uq))
                lc <- qVals[[1]]
                uc <- qVals[[2]]
                deList[[comp]] <- rownames(deg.list.comp)[which(deg.list.comp$score <= lc | deg.list.comp$score >= uc)]
        }
        deGenes <- unique(unlist(deList))

        dataColsVarI <- phTable[,varI]

        tmp.data <- data
        colnames(tmp.data) <- phTable[, params$gVars$sampleColID]

        selCols <- which(dataColsVarI %in% conditions)
        selRows <- which(rownames(tmp.data) %in% deGenes)

        tmp.data.sel <- tmp.data[selRows, selCols]
        dataColsVarI.sel <- dataColsVarI[which(dataColsVarI %in% conditions)]
        classPalette <- setNames(randomcoloR::distinctColorPalette(length(conditions)), conditions)

        res <- heatplot(tmp.data.sel, 
                dend = "column", 
                scale = "none", 
                cols.default=F, 
                lowcol="yellow", 
                highcol="red", 
                cexCol=1, 
                margins=c(8,16), 
                labRow=rownames(tmp.data.sel), 
                classvec=dataColsVarI.sel, 
                #classvecCol=c(1:length(conditions))
                classvecCol=classPalette
        )
        par(lend = 1)           # square line ends for the color legend
        legend("bottomleft",      # location of the legend on the heatmap plot
                legend = conditions, # category labels
                #col = c(1:length(conditions)),  # color key
                col = classPalette,
                bty = "n",
                bg = "white",
                border = "white",
                cex = .7,
                lty= 1,            # line style
                lwd = 10           # line width
        )
}else{
        print("Differential results not found!")
}
```
